---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

WIP WIP WIP WIP WIP WIP

# tweetview

Tools to Organize and Visualize Tweets Including Tweet Threads

## Description

## What's Inside The Tin

The following functions are implemented:

- `as_tweet_thread`:	Turn a data frame of 'rtweet' tweets into a tweet thread
- `get_thread`:	Retrieve an authors tweet thread/rant from a starting status id
- `htmlify_tweet`:	Make a Tweet into an HTML object
- `print.tweet_thread`:	Print method for a tweet thread
- `style_tweet`:	Style a tweet with HTML

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/tweetview")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(tweetview)
library(tidyverse)

# current verison
packageVersion("tweetview")

```

```{r cache=TRUE}
thrd <- get_thread("988895496381984770")

thrd

str(thrd, 1)

glimpse(thrd$tweet_thread)
```

There's a vanilla HTML-ified version of that text in `$thread_html`. Run this to see it and you can add your own CSS styling. The vignette source has some example CSS.

```{r eval=FALSE}
htmltools::html_print(htmltools::HTML(thrd$thread_html))
```